Scheeper's Meager-NWD Game and the Menger Game

### 2014-08-25 phd/dissertation/_raw_chapter5.tex
Name and camelCase based game commands/definitions

\begin{question}
$K \prewin G_{K,L}(X) \Rightarrow X$ is a $k$-space?
\end{question}

\centerline{\bf Another game: $Con_{O,P}(X,x)$}

\begin{definition} 
Gruenhage's open-point convergence game $Con_{O,P}(X,x)$ has $O$ choosing nested open sets and $P$ choosing a point within the last chosen open set by $O$. $O$ wins if the points chosen by $P$ converge to $x$.
\end{definition}

\begin{definition}
The one-point compactification of a space $X$ is $X\cup\{\infty\}$, where neighborhoods of points in $X$ are the same as they were originally, and neighborhoods of $\infty$ are sets $X\cup\{\infty\}\setminus K$ for compact $K$. If $X$ is discrete then neighborhoods of $\infty$ are cofinite sets containing $\infty$. 
\end{definition}

\begin{proposition}
$O\not\prewin Con_{O,P}(\kappa\cup\{\infty\},\infty)$, where $\kappa\cup\{\infty\}$ is the one-point compactification of discrete $\kappa\geq\omega_1$.
\end{proposition}

\begin{proof}
Given a predetermined strategy $\sigma(n)$ for $O$, $P$ simply chooses any ordinal in $\bigcap_{n<\omega} \sigma(n)$ to play on every turn.
\end{proof}

\begin{definition}
A \textbf{coding strategy} considers only the most recent move by each player. If Player $Z$ has a winning coding strategy for a game $G$, this may be denoted $Z \codewin G$.
\end{definition}

\begin{proposition}
$O\codewin Con_{O,P}(\kappa\cup\{\infty\},\infty)$ for any cardinal $\kappa$. 
\end{proposition}

\begin{proof}
Define $\sigma(U,p)=U\setminus\{p\}$. A legal play by $P$ must never repeat the same point, so legal plays by $P$ converge to $\infty$.
\end{proof}

\begin{proposition}
$O\not\tactwin Con_{O,P}(\kappa\cup\{\infty\},\infty)$ for $\kappa\geq\omega_1$.
\end{proposition}

\begin{proof}
Let $F(\alpha)$ be the complement of a tactical strategy for $O$. There exists some $n<\omega$ such that we may find an infinite $B\subseteq \omega_1$ with $n\not\in F(\beta)$ for $\beta\in B$ - if not, we may find uncountable ordinals $\alpha$ such that $\omega \subseteq F(\alpha)$, a contradiction. Choose $\beta\in B\setminus F(n)$, and note that repeating $n,\beta$ is a successful counter to $O$'s strategy.
\end{proof}

\begin{definition}
A \textbf{$k$-tactical strategy} considers only the last $k$ moves by the opposing player. If Player $Z$ has a winning $k$-tactical strategy for a game $G$, this may be denoted $Z \ktactwin{k} G$.
\end{definition}

\begin{theorem}
$O\not\ktactwin{k}Con_{O,P}(\kappa\cup\{\infty\},\infty)$ for $\kappa\geq\omega_1$.
\end{theorem}

\begin{proof}
Let $\sigma:[\omega_1]^{\leq k}\to[\omega_1]^{<\omega}$ be a $k$-tactical strategy for $O$ restricted to $\omega_1$ and $F(S)=\omega_1\setminus\sigma(S)$.

Let $W_0=\omega_1$. We define $W_\alpha$ recursively as follows:
    \begin{itemize}
    \item For successor ordinals $\alpha+1$, let $\beta$ be the least element of $W_\alpha$ such that $[\beta+1,\omega_1) \cap \bigcup_{S\leq \beta} F(S)$ is nonempty, where $S \leq \beta$ is shorthand for $\{S \in [\omega_1]^{\leq k} : \forall \gamma \in S(\gamma < \beta)\}$. If no such $\beta$ exists, let $W_{\alpha+1}=W_\alpha$ and otherwise let $W_{\alpha+1}=W_\alpha \setminus \left([\beta+1,\omega_1) \cap \bigcup_{S\leq \beta} F(S)\right)$.
    \item For limit ordinals $\alpha$, let $W_\alpha = \bigcap_{\beta<\alpha} W_\beta$.
    \end{itemize}

Finally let $W=\bigcap_{\alpha<\omega_1}W_\alpha$ and observe that it is unbounded. Let $R$ collect all ordinals $\alpha\in W$ such that there is an ordinal $\beta$ where for all $S\in[W\cap(\beta,\omega_1)]^{\leq k}$, $\alpha \in F(S)$. It is easily seen that $R$ is finite. Let $0^*$ be the least element of $W\setminus R$.

Now, define a strictly increasing sequence of ordinals $\left<\alpha_1,\alpha_2,\alpha_3,\alpha_4,\dots\right>$ such that $\alpha_i \in W$ and $0^* \not\in F(\{\alpha_{2i+1},\dots,\alpha_{2i+k}\})$ for all $i$. The play $\left<0^*,\alpha_1,\dots,\alpha_k,0^*,\alpha_{k+1},\dots,\alpha_{2k},0^*,\dots\right>$ then defeats the strategy $\sigma$.
\end{proof}

Peter J. Nyikos has shown the following:

\begin{theorem}
$O\not\markwin Con_{O,P}(\omega_1\cup\{\infty\},\infty)$.
\end{theorem}

This can be improved:

\begin{theorem}
$O\not\kmarkwin{k} Con_{O,P}(\kappa\cup\{\infty\},\infty)$ for $\kappa\geq\omega_1$.
\end{theorem}

\begin{proof}
Let $F:[\omega_1]^{\leq k}\times\omega\to[\omega_1]^{<\omega}$ be the complement of a $k$-Markov strategy for $O$ restricted to $\omega_1$.

Let $W_0=\omega_1$. We define $W_\alpha$ recursively as follows:
    \begin{itemize}
    \item For successor ordinals $\alpha+1$, let $\beta$ be the least element of $W_\alpha$ such that \[(\beta,\omega_1) \cap \bigcup_{S\in [\beta]^{\leq k}, n<\omega} F(S,n)\] is nonempty. If no such $\beta$ exists, let $W_{\alpha+1}=W_\alpha$ and otherwise let \[W_{\alpha+1}=W_\alpha \setminus \left((\beta,\omega_1) \cap \bigcup_{S\in[\beta]^{\leq k}, n<\omega} F(S,n)\right)\]
    \item For limit ordinals $\alpha$, let $W_\alpha = \bigcap_{\beta<\alpha} W_\beta$.
    \end{itemize}

Finally let $W=\bigcap_{\alpha<\omega_1}W_\alpha$ and observe that it is unbounded. Let $R$ collect all ordinals $\alpha\in W$ such that there is an ordinal $\beta_\alpha$ and number $n_\alpha<\omega$ where for all $S\in[W\cap(\beta_\alpha,\omega_1)]^{\leq k}$, $\alpha \in F(S,n_\alpha)$.

If $R$ was infinite, then there is $\alpha_i\in R$ for each $i<\omega$ and some $N<\omega$ where for all $S\in[W\cap(\beta_{\alpha_i},\omega_1)]^{\leq k}$, $\alpha_i \in F(S,N)$, and thus for all $S\in[W\cap(\sup \beta_{\alpha_i},\omega_1)]^{\leq k}$,  $\{\alpha_i : i<\omega\} \subset F(S,N)$, a contradiction. So let $0^*$ be the least element of $W\setminus R$.

Now, define a strictly increasing sequence of ordinals $\left<\alpha_1,\alpha_2,\alpha_3,\alpha_4,\dots\right>$ such that $\alpha_i \in W$ and $0^* \not\in F(\{\alpha_{2i+1},\dots,\alpha_{2i+k}\})$ for all $i$. The play $\left<0^*,\alpha_1,\dots,\alpha_k,0^*,\alpha_{k+1},\dots,\alpha_{2k},0^*,\dots\right>$ then defeats the Markov strategy.
\end{proof}

While these counters prevent convergence to $\infty$, they do not prohibit clustering, as any sequence of points with infinite range clusters at $\infty$ in this space.

\begin{definition} 
The open-point clustering game $Clus_{O,P}(X,x)$ has $O$ choosing nested open sets and $P$ choosing a point within the last chosen open set by $O$. $O$ wins if the points chosen by $P$ cluster to $x$.
\end{definition}

Any strategy which forces convergence also forces clustering, so a coding strategy exists for player $O$. And since the counter used above to foil any tactical strategy had only finite range...

\begin{proposition}
$O\not\tactwin Clus_{O,P}(X,\infty)$.
\end{proposition}

The other counters only attempt to repeat a point infinitely often, and may have infinite range.

\begin{example}
For $\omega\leq\alpha<\omega_1$ let $\leq_{\alpha}$ be a well-ordering of $\omega_1$ such that its restriction to $\alpha$ is isomorphic to $\omega$ with isomorphism $f(n):\omega\to\alpha$. For $n<\omega$ let $\leq_n$ simply be $\leq$ and $f$ be the identity.

The 2-tactical strategy for $O$ in $Clus_{O,P}(\omega_1\cup\{\infty\}),\infty)$ whose complement is, for $\alpha<\beta$, $F(\alpha,\beta)=\{\gamma : \gamma \leq_\beta \alpha \} \cup \{\beta\}$, forces the point-picker to chose more than three distinct points.
\end{example}

\begin{proof}
Suppose Player $P$ started with $\alpha_0<\alpha_1$. Player $O$ forbids \[F(\alpha_0,\alpha_1) = \{\gamma : \gamma \leq_{\alpha_1}\alpha_0\} \cup \{\alpha_1\}\] so Player $P$ must respond with $\alpha_2$ such that either $\alpha_0<\alpha_1<\alpha_2$ or $\alpha_0<_{\alpha_1}\alpha_2<\alpha_1$.

In the first case that $\alpha_0<\alpha_1<\alpha_2$, Player $O$ now forbids \[F(\alpha_1,\alpha_2) = \{\gamma : \gamma \leq_{\alpha_2}\alpha_1\} \cup \{\alpha_2\}\] If $\alpha_0<_{\alpha_2}\alpha_1$ we're done. Otherwise, Player $P$ chooses $\alpha_0>_{\alpha_2}\alpha_1$ again, and Player $O$ responds with \[F(\alpha_0,\alpha_2)=\{\gamma : \gamma \leq_{\alpha_2} \alpha_0 \} \cup \{\alpha_2\}\] which successfully forbids $\alpha_1$.

In the second case that $\alpha_0<_{\alpha_1}\alpha_2<\alpha_1$, Player $O$ forbids \[F(\alpha_1,\alpha_2) = \{\gamma : \gamma \leq_{\alpha_1}\alpha_2\} \cup \{\alpha_1\}\] which successfully forbids $\alpha_0$.

Thus, a fourth ordinal must be selected.
\end{proof}

But the fourth ordinal is all that is needed.

\begin{theorem}
$O\not\ktactwin{2}Clus_{O,P}(\omega_1\cup\{\infty\},\infty)$.
\end{theorem}

\begin{proof}
Let $F(\alpha,\beta)$ be the complement of a k-tactical strategy for O, and assume without loss of generality that it does not forbid any ordinals larger than its inputs.

Let $n_0=\min(\omega\setminus F(\emptyset)\setminus F(\omega,\omega+1))$ and $n_1 = \min(\omega\setminus F(n_0)\setminus F(n_0,\omega+1))$.

It follows that $\left<n_0,n_1,\omega,\omega+1,n_0,n_1,\omega,\omega+1,\dots\right>$ is a legal counter.
\end{proof}

But, in fact, a similar counter can be used for any $k$-tactical strategy.

\begin{theorem}
$O\not\ktactwin{k}Clus_{O,P}(\omega_1\cup\{\infty\},\infty)$.
\end{theorem}

\begin{proof}
Let $F(\alpha_0,\dots,\alpha_{k-1})$ be the complement of a k-tactical strategy for O, and assume without loss of generality that it does not forbid any ordinals larger than its inputs.

For $0\leq i < k$, we define \[n_i = \min(\omega\setminus F(n_0,\dots,n_{i-1},\omega+i,\dots,\omega+k-1)\setminus F(n_0,\dots,n_{i-1}))\]

It follows that $\left<n_0,\dots,n_{k-1},\omega,\dots,\omega+k-1,n_0,\dots,n_{k-1},\omega,\dots,\omega+k-1,\dots\right>$ is a legal counter.
\end{proof}

However, a Markov strategy is sufficient to defeat $P$ in the clustering game for $\omega_1$.

\begin{theorem}
$O\markwin Clus_{O,P}(\omega_1\cup\{\infty\},\infty)$.
\end{theorem}

\begin{proof}
For $\omega\leq\alpha<\omega_1$ let $\leq_{\alpha}$ be a well-ordering of $\omega_1$ such that its restriction to $\alpha$ is isomorphic to $\omega$ with isomorphism $f(n):\omega\to\alpha$. For $n<\omega$ let $\leq_n$ simply be $\leq$ and $f$ be the identity.

Let $F(\alpha,n)=\{\gamma : \gamma \leq_\alpha f(n)\}$ be the complement of $O$'s Markov strategy in response to move $\alpha$ in round $n$.

If a legal counter by $P$ does not repeat some largest ordinal infinitely often, it does not result in a win for $P$. Otherwise let $\beta$ be largest ordinal repeated infinitely often in some legal counter by $P$. We note that the forbidden sets responded by $O$ are of the form $F(\beta,n)$ where $n$ increases as the game progresses. It is impossible to repeat any ordinal less than $\beta$ infinitely often due to the increasing round number, so the range of the counter is infinite, and does not result in a win for $P$.
\end{proof}

...while it similarly fails for $\kappa>\omega_1$.

\begin{theorem}
$O\not\kmarkwin{k}Clus_{O,P}(\kappa\cup\{\infty\},\infty)$ for $\kappa>\omega_1$.
\end{theorem}

\begin{proof}
Let $F:\omega\times[\kappa]^{\leq k} \to [\kappa]^\omega$ be the complement of a k-Markov strategy for O, and assume without loss of generality that it does not forbid any ordinals larger than its inputs.

For $0\leq i < k$, we define \[\beta_i = \min(\omega\setminus \bigcup_{n<\omega} F(n,\{\beta_0,\dots,\beta_{i-1},\omega_1+i,\dots,\omega_1+k-1\})\setminus\bigcup_{n<\omega} F(n,\{\beta_0,\dots,\beta_{i-1}\}))\]

It follows that $\left<\beta_0,\dots,\beta_{k-1},\omega_1,\dots,\omega_1+k-1,\beta_0,\dots,\beta_{k-1},\omega_1,\dots,\omega_1+k-1,\dots\right>$ is a legal counter.
\end{proof}

\centerline{\bf $Con_{O,P}(X,x)$ for Sigma Product}

\begin{proposition}
The player $O$ has a winning strategy for $Con_{O,P}(X,x)$ where \[X=\Sigma\mathbb{R}^{\omega_1}=\{x\in \mathbb{R}^{\omega_1}: x_\alpha = 0 \text{ for all but countably many } \alpha<\omega_1\}\]
\end{proposition}

\begin{proof}
Without loss of generality we may assume that $x$ is the zero function. Let $y_n$ be the move by $P$ on turn $n$. For each $y_n$, let $l_n\in \omega_1^{\omega}$ enumerate the nonzero coordinates in $y_n$. Give $O$ the strategy $\sigma(y_0,\dots,y_{n-1}) = \prod_{\alpha<\omega_1} O_\alpha$ where if $\alpha$ is listed in the first $n$ coordinates of any term in $\left<l_k\right>_{k<n}$, then $O_\alpha=(-2^{-n},2^{-n})$, and $O_\alpha=\mathbb{R}$ otherwise.
\end{proof}

\begin{theorem}
For all cardinals $\kappa\leq 2^\omega$, the player $O$ has a winning coding strategy for $Con_{O,P}(X,x)$ where \[X=\Sigma\mathbb{R}^{\kappa}=\{x\in \mathbb{R}^{\kappa}: x_\alpha = 0 \text{ for all but countably many } \alpha<\kappa\}\]
\end{theorem}

\begin{proof}
Note that $|\Sigma\mathbb{R}^\kappa| \leq 2^\omega = |\mathbb{R}|$. Define the following:

    \begin{itemize}
    \item Encode every finite sequence $s$ of functions in $\Sigma\mathbb{R}^{\kappa}$ as a real number $0<r(s)<1$. 
    \item Let $\gamma(U)$ be the function which, for basic open sets $U=\prod_{\alpha<\kappa}U_\alpha$ where $U_0=(-\frac{1}{R},\frac{1}{R})$ for some positive noninteger real number $R$, returns the sequence $r^{-1}(R-\lfloor R\rfloor)$.
    \item Let $n(U)$ be the length of $\epsilon^{-1}(\gamma(U))$.
    \item Let $\psi(U,y)=\epsilon^{-1}(\gamma(U))^\frown\left<y\right>$.
    \item Define $\sigma_0(U,y)$ to be $\left(-\frac{1}{n(U)+r(\psi(U,y))},\frac{1}{n(U)+r(\psi(U,y))}\right)$.
    \item For each $0<\alpha<\kappa$, define the interval $\sigma_\alpha(U,y)$ about $0$ as follows:
        \begin{itemize}
        \item If $\alpha$ is listed in the first $n(U)$ coordinates of any term in the finite sequence $\psi(U,y)$, then $\sigma_\alpha(U,y)=(-\frac{1}{n(U)+1},\frac{1}{n(U)+1})$.
        \item Otherwise, then $\sigma_\alpha(U,y)=\mathbb{R}$.
        \end{itemize}
    \end{itemize}

It follows that $\sigma(U,y)=\prod_{\alpha<\kappa} \sigma_\alpha(U,y)$ is a winning coding strategy.
\end{proof}

\begin{theorem}
For all cardinals $\kappa>2^\omega$ such that $\kappa^\omega = \kappa$, the player $O$ has a winning coding strategy for $Con_{O,P}(X,x)$ where \[X=\Sigma\mathbb{R}^{\kappa}=\{x\in \mathbb{R}^{\kappa}: x_\alpha = 0 \text{ for all but countably many } \alpha<\omega_1\}\]
\end{theorem}

\begin{proof}
Note that $|\Sigma\mathbb{R}^\kappa| = \kappa^\omega = \kappa$. Define the following:

>>>>

\begin{ques}
$K \prewin G_{K,L}(X) \Rightarrow X$ is a $k$-space?
\end{ques}

\section{Cantor space example}

\begin{ex}
Let $X$ be a zero-dimensional, compact L-space (hereditarally Lindeloff and non-separable). It is a fact that there exists a point-countable collection $\mathcal{U}=\{U_\alpha : \alpha<\omega_1\}$ of clopen sets in $X$, and it is also true that any point-finite subcollection of $\mathcal{U}$ is countable. %That is, if we let $A_x = \{\alpha : x \in U_\alpha\}$, then $|A_x|\leq\omega$ for all $x\in X$.

Let $C = \{c_\alpha : \alpha <\omega_1\}$ be any uncountable subset of the Cantor space $2^\omega$. Let $X_s = X \times \{s\}$ for each $s \in 2^{<\omega}$, and $U_{\alpha,s} = U_\alpha \times \{s\}$.

Finally, let \[\mathbb{X} = C \cup \bigcup_{s\in 2^{<\omega}} X_s\] be a tree of $2^{<\omega}$ copies of $X$, and where \[c_\alpha \cup \bigcup_{n < \omega} U_{\alpha, x_\alpha \restriction n}\] is an open set about each $c_\alpha$.
\end{ex}

\begin{defn}
Let $S\in[\omega_1]^{<\omega}$ and $m<\omega$. Define
    \[K_S = \bigcup_{\alpha \in S} \left( c_\alpha \cup \left(\bigcup_{s < c_\alpha} U_{\alpha,s}\right)\right)\]
    \[ A = \{z^\frown \<1\> : z \in 1^{<\omega}\}\]
    \[ K^*_S = K_S \setminus \bigcup_{s \in A} X_s \]
and
    \[L_m = \bigcup_{s \in 2^{<m}} X_s\]
and observe that every compact set is dominated by $K^*_S \cup L_m$ for some $S,m$. Intuitively, $K^*_S$ collects the branches of $U_\alpha$ converging up to $c_\alpha$ for each $\alpha \in S$ while avoiding copies $X_s$ of $X$ for each $s$ in an antichain $A$, and $L_m$ collects the copies $X_s$ of $X$ with $|s| < m$ at the base of the tree.
\end{defn}

\begin{prop}
Without loss of generality, $P$ always plays points in $\bigcup_{s \in 2^{<\omega}} X_s$.
\end{prop}

\begin{prop}
$K \win \gruKPGame{\mathbb{X}}$.
\end{prop}

\begin{proof}
In response to a point $\<x,s\>$, $K$ observes that there are only countably many $\alpha$ such that $U_\alpha \times \{s\}$ contains $\<x,s\>$ (by point-countability of $X$). Enumerate these as $\alpha_n$. $K$ makes a promise that during round $m$, $K$ will forbid some superset of $K_{\{\alpha_n : n\leq m\}}$. Finally, $K$ also always forbids a superset of $L_{|s|+1}$.

Suppose $P$'s moves clustered at some point. Since $K$ forbade $L_{|s|+1}$ during each round, that point must be $c_\alpha$ for some $\alpha$. $P$'s play then must have included a subsequence of points $\<x_0,s_0\>,\<x_1,s_1\>,\<x_2,s_2\>\dots$ such that $x_n \in U_\alpha$ and $s_n \leq s_{n+1} \leq c_\alpha$. However, in response to $\<x_0,s_0\>$, $K$ made a promise to eventually forbid a superset of $K_{\{\alpha\}}$, making every $\<x_n,t_n\>$ illegal after that round.
\end{proof}

\begin{thm}
$K\not\tactwin\gruKPGame{\mathbb{X}}$.
\end{thm}

\begin{proof}
This is actually a corollary of G's theorem in [?]. The following is a direct game-theoretic proof.

Suppose that $\sigma(\<x,s\>)$ was a winning strategy for $K$ and assume
  \[
    \sigma(\<x,s\>) = \bigcup_{|t|\leq |s|} \sigma(\<x,t\>) = \sigma'(x,|s|)
  \]
Thus there exists some $f: \omega_1 \to \omega$ such that $\sigma'(x,f(\alpha))$ covers every neighborhood of $c_\alpha$ for all $x\in U_\alpha$. (If not, $P$ wins by taking the $\alpha$ for which $f$ is not defined, and may always play $\<x,s\>$ in a neighborhood of $c_\alpha$ for which $\sigma'(x,|s|)$ doesn't cover a neighborhood of $c_\alpha$.) Fix $n$ for which $f(\alpha)=n$ for $\alpha$ in an uncountable set $A$.

Since the collection $\{U_\alpha : \alpha \in A\}$ is uncountable, it is not point-finite. Fix $x$ so that $x$ belongs to $U_\alpha$ for all $\alpha$ in an infinite $B \subseteq A$. Finally, consider $\sigma'(x,n)$. For each $\alpha\in B$, $\sigma'(x,f(\alpha))=\sigma'(x,n)$ covers $c_\alpha$. Since $\{c_\alpha : \alpha \in B\}$ is a closed infinite discrete set, we have a contradiction to the compactness of $\sigma'(x,n)$.
\end{proof}

\begin{thm}
$K\not\ktactwin{2}\gruKPGame{\mathbb{X}}$.
\end{thm}

\begin{proof}
Suppose $\sigma(\<x,s\>,\<y,t\>)$ was a winning 2-tactical strategy. We may define $S(x,y,n)\in [\omega_1]^{<\omega}$ (increasing on $n$) and $n<m(x,y,n)<\omega$ such that for each $(x,y)$,
  \[
    \bigcup_{s,t \in 2^{\leq n}} \sigma(\<x,s\>,\<y,t\>) \subseteq
    K^*_{S(x,y,n)} \cup L_{m(x,y,n)}
  \]
and so we assume
  \[
    \sigma(\<x,s\>,\<y,t\>) =
    K^*_{S(x,y,\max(|s|,|t|))} \cup L_{m(x,y,\max(|s|,|t|))}
  \]

Select an arbitrary point $x' \in X$. We define a tactical strategy
  \[
  \tau(x,s) =
  K^*_{S(x,x',m(x,x',|s|)+1)} \cup L_{m(x,x',m(x,x',|s|)+1)}
  \]
We complete the proof by showing $\tau$ is a winning tactical strategy (a contradiction).

Suppose
\[
\<x_0, s_0\>, \<x_1, s_1\>, \<x_2, s_2\>, \dots
\]
successfully countered $\tau$ by clustering at $c\in C$ (the strategy trivially prevents clustering elsewhere). Let $z_n = \<0,\dots,0\>$ with $n$ zeros. We claim
\[
\<x_0, s_0\>, \<x', {z_{m(x_0,x',|s_0|)}}^\frown\<1\>\>, \<x_1, s_1\>, \<x', {z_{m(x_1,x',|s_1|)}}^\frown\<1\>\>,  \<x_2, s_2\>, \<x', {z_{m(x_2,x',|s_2|)}}^\frown\<1\>\>, \dots
\]
is a successful counter to $\sigma$.

We will need the fact that, as $\<x_{i+1},s_{i+1}\>$ was legal against $\tau$:
  \[
    |s_i| <
    m(x_i,x',|s_i|)+1 =
    |{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|
  \]
  \[
    <
    m(x_i,x',m(x_i,x',|s_i|)+1) =
    m(x_i,x',|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|) \leq
    |s_{i+1}|
  \]

Note that $m(x,y,\max(|s|,|t|))$ is increasing throughout this play of the game versus $\sigma$:
  \[
    m(x_i,x',\max(|s_i|,|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|))
  \]
  \[
    =
    m(x_i,x',|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|)
  \]
  \[
    \leq
    |s_{i+1}|
  \]
  \[
    <
    m(x_{i+1},x',|s_{i+1}|)
  \]
  \[
    =
    m(x_{i+1},x',\max(|s_{i+1}|,|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|))
  \]
  \[
    =
    |{z_{m(x_{i+1},x',|s_{i+1}|)}}|
  \]
  \[
    <
    |{z_{m(x_{i+1},x',|s_{i+1}|)}}^\frown\<1\>|
  \]
  \[
    <
    m(x_{i+1},x',|{z_{m(x_{i+1},x',|s_{i+1}|)}}^\frown\<1\>|)
  \]
  \[
    =
    m(x_{i+1},x',\max(|s_{i+1}|,|{z_{m(x_{i+1},x',|s_{i+1}|)}}^\frown\<1\>|))
  \]

We turn to showing that $\<x', {z_{m(x_{i+1},x',|s_{i+1}|)}}^\frown\<1\>\>$ is always a legal move. Since ${z_{m(x_{i+1},x',|s_{i+1}|)}}^\frown\<1\>$ is on the antichain avoided by any $K^*$, the problem is reduced to showing that this move isn't forbidden by
  \[
  L_{m(x_{i+1},x',\max(|s_{i+1}|,|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|))}
  \]
which we can see here:
  \[
    m(x_{i+1},x',\max(|s_{i+1}|,|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|)) =
    m(x_{i+1},x',|s_{i+1}|) <
    |{z_{m(x_{i+1},x',|s_{i+1}|)}}^\frown\<1\>|
  \]

We can conclude by showing that $\<x_{i+1},s_{i+1}\>$ is always a legal move. We can see it avoids
  \[
  L_{m(x_{i},x',\max(|s_{i}|,|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|))}
  \]
since
  \[
    m(x_{i},x',\max(|s_{i}|,|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|)) =
    m(x_{i},x',|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|) \leq
    |s_{i+1}|
  \]

Since $\<x_{i+1},s_{i+1}\>$ was legal against $\tau$, it avoided
  \[
    K^*_{S(x_h,x',m(x_h,x',|s_h|)+1)} =
    K^*_{S(x_h,x',\max(|s_h|,|{z_{m(x_h,x',|s_h|)}}^\frown\<1\>|))}
  \]
for $h\leq i$. And when $h<i$, we see it avoids:
  \[
    K^*_{S(x_{h+1},x',\max(|s_{h+1}|,|{z_{m(x_h,x',|s_h|)}}^\frown\<1\>|))} =
    K^*_{S(x_{h+1},x',|s_{h+1}|)}
  \]
  \[
    \subseteq
    K^*_{S(x_{h+1},x',m(x_{h+1},x',|s_{h+1}|)+1)}
  \]

This concludes the proof.
\end{proof}

\begin{thm}
$K\not\ktactwin{k}\gruKPGame{\mathbb{X}}$.
\end{thm}

\begin{proof}
The proof proceeds in parallel to the proof of $K\not\ktactwin{2}\gruKPGame{\mathbb{X}}$.

Suppose $\sigma(\<x_0,s_0\>,\dots,\<x_{k},s_{k}\>)$ was a winning $(k+1)$-tactical strategy. We may define $S(x_0,\dots,x_{k},n)\in [\omega_1]^{<\omega}$ (increasing on $n$) and $n<m(x_0,\dots,x_{k},n)<\omega$ such that for each $(x_0,\dots,x_{k})$,
  \[
    \bigcup_{s_0,\dots,s_k \in 2^{\leq n}} \sigma(\<x_0,s_0\>,\dots,\<x_{k},s_{k}\>) \subseteq
    K^*_{S(x_0,\dots,x_{k},n)} \cup L_{m(x_0,\dots,x_{k},n)}
  \]
and so we assume
  \[
    \sigma(\<x_0,s_0\>,\dots,\<x_{k},s_{k}\>) =
    K^*_{S(x_0,\dots,x_{k},\max(|s_0|,\dots,|s_k|))} \cup L_{m(x_0,\dots,x_{k},\max(|s_0|,\dots,|s_k|))}
  \]

Select an arbitrary point $x' \in X$. Let $M^0(x,n)=m(x,x',\dots,x',n)$ and $M^{i+1}(x,n)=M^0(x,M^i(x,n)+1)$. We define a tactical strategy
  \[
  \tau(x,s) = K^*_{S(x,x',\dots,x',M^{k-1}(x,|s|)+1)} \cup L_{m(x,x',\dots,x',M^{k-1}(x,|s|)+1)}
  \]
We complete the proof by showing $\tau$ is a winning tactical strategy (a contradiction).

Suppose
\[
\<x_0, s_0\>, \<x_1, s_1\>, \<x_2, s_2\>, \dots
\]
successfully countered $\tau$ by clustering at $c\in C$ (the strategy trivially prevents clustering elsewhere). Let $z_n = \<0,\dots,0\>$ with $n$ zeros. We claim
\[
  \<x_0, s_0\>,
  \<x', {z_{M^0(x_0,|s_0|)}}^\frown\<1\>\>,
  \<x', {z_{M^1(x_0,|s_0|)}}^\frown\<1\>\>,
  \dots,
  \<x', {z_{M^{k-1}(x_0,|s_0|)}}^\frown\<1\>\>,
\]
\[
  \<x_1, s_1\>,
  \<x', {z_{M^0(x_1,|s_1|)}}^\frown\<1\>\>,
  \<x', {z_{M^1(x_1,|s_1|)}}^\frown\<1\>\>,
  \dots,
  \<x', {z_{M^{k-1}(x_1,|s_1|)}}^\frown\<1\>\>,
  \dots
\]
is a successful counter to $\sigma$.

We will need the fact that, as $\<x_{i+1},s_{i+1}\>$ was legal against $\tau$:
  \[
    |s_i| <
    M^0(x_i,|s_i|)+1 =
    |{z_{M^0(x_i,|s_i|)}}^\frown\<1\>| <
    M^0(x_i,M^0(x_i,|s_i|)+1)+1
  \]
  \[
    =
    M^1(x_i,|s_i|)+1 =
    |{z_{M^1(x_i,|s_i|)}}^\frown\<1\>| <
    \dots <
    |{z_{M^{k-1}(x_i,|s_i|)}}^\frown\<1\>|
  \]
  \[
    =
    M^{k-1}(x_i,|s_i|) + 1 <
    m(x_i,x',\dots,x',M^{k-1}(x_i,|s_i|)+1) \leq
    |s_{i+1}|
  \]

Note that $m(x_0,\dots,x_{k},\max(|s_0|,\dots,|s_k|))$ is increasing throughout this play of the game versus $\sigma$:
  \[
    m(x_i,x',\dots,x',\max(|s_i|,|{z_{M^0(x_i,|s_i|)}}^\frown\<1\>|,\dots,|{z_{M^{k-1}(x_i,|s_i|)}}^\frown\<1\>|))
  \]
  \[
    =
    m(x_i,x',\dots,x',|{z_{M^{k-1}(x_i,|s_i|)}}^\frown\<1\>|)
  \]
  \[
    =
    m(x_i,x',\dots,x',M^{k-1}(x_i,|s_i|)+1)
  \]
  \[
    \leq
    |s_{i+1}|
  \]
  \[
    <
    M^0(x_{i+1},|s_{i+1}|)
  \]
  \[
    =
    m(x_{i+1},x',\dots,x',|s_{i+1}|)
  \]
  \[
    =
    m(x_{i+1},x',\dots,x',\max(|s_{i+1}|,|{z_{M^0(x_i,|s_i|)}}^\frown\<1\>|,\dots,|{z_{M^{k-1}(x_i,|s_i|)}}^\frown\<1\>|))
  \]
  \[
    =
    |{z_{m(x_{i+1},x',\dots,x',|s_{i+1}|)}}|
  \]
  \[
    =
    |{z_{M^0(x_{i+1},|s_{i+1}|)}}|
  \]
  \[
    <
    |{z_{M^0(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|
  \]
  \[
    <
    m(x_{i+1},x',\dots,x',|{z_{M^0(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|)
  \]
  \[
    =
    m(x_{i+1},x',\dots,x',\max(|s_{i+1}|,|{z_{M^0(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|,|{z_{M^1(x_{i},|s_{i}|)}}^\frown\<1\>|,\dots,|{z_{M^{k-1}(x_{i},|s_{i}|)}}^\frown\<1\>|))
  \]
  \[
    \vdots
  \]
  \[
    <
    m(x_{i+1},x',\dots,x',\max(|s_{i+1}|,|{z_{M^0(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|,\dots,|{z_{M^{k-1}(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|))
  \]
